Report on Certificate Tools

### 2016-08-31 TEX/draft.tex
More text added

@@

>>>>

      \paragraph{Specify Type}
With keytool alone it is not possible to make CA certificate.
      \paragraph{Specify path length}
Specifying of path length is not availiable.
  \subsection{Specifications}

    \subsubsection{Certificate Signing Request signing}
Keytool cannot be used to sign Certificate Signing Request.
    \subsubsection{Create combination of private key and signed chain}

    \subsubsection{Specify certificate validity}
Specification of certificate validity is set when generating key pair in \verb+-validity [time]+ option.
    \subsubsection{Setting Subject Alternative Name for end certificates}
To set a Subject Alternative Name for certificate use \verb+-ext san=dns:www.dnsexample.com,ip:1.1.1.1+ which will add SAN to certificate   
    \subsubsection{Support for Cryptographic Service Provider}

@@

    \subsubsection{Private key only}
Exporting of private key only is not availiable in keytool.
  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
